---
title: "ISQS-7339-sim-project-case-2"
author: "TQ Senkungu"
date: "4/26/2020"
output: word_document
---


import the data frame with project data

```{r}
sturgill_manu <- read.csv("https://raw.githubusercontent.com/tikisen/ISQS-7339-sim-project/master/Case%202/sturgill_manu.csv")

set.seed(1234)
nsim = 100000
demands <-c(42,18,6,6,6,6)

part.time<- function(demand, mean, sd){
  total.time <- 0
  for (i in 1:length(demand)){
    total.time <- total.time + demand*rnorm(nsim, mean, sd)
  }
  return(total.time)
}
```

calculate weekly capacity 

```{r}
capacity <- 120*rnorm(nsim, .7, .05)
capacity.mean <- mean(capacity)
capacity.mean
capacity.sd <- sd(capacity)
capacity.sd

```

caclulate time for all parts for each machine

First calculate the values for machine A

```{r}
# machine A
# import means and sds for manufacturing time for parts in machine A
means.A <- sturgill_manu$Machine.A.avg
sds.A <- sturgill_manu$Machine.A.sd

# calculate rnorm for all parts on machine A
time.A <- part.time(demands, means.A, sds.A)
mean(time.A)
sd(time.A)

# calculate number of machines needed
machine.A = time.A/capacity

# mean and sd for numbers of machines A 
mean.machine.A <- mean(machine.A)
mean.machine.A

sd.machine.A <- sd(machine.A)
sd.machine.A

hist(machine.A)
```

With a mean of 3.4 machines needed to meet demand, we recommend having 4 of Machine A.

Next, calculate values for machine B.

```{r}
# machine B
# import means and sds for manufacturing time for parts in machine A
means.B <- sturgill_manu$Machine.B.avg
sds.B <- sturgill_manu$Machine.B.sd

# calculate rnorm for all parts on machine B
time.B <- part.time(demands, means.B, sds.B)
mean(time.B)
sd(time.B)

# calculate number of machines needed
machine.B = time.B/capacity

# mean and sd for numbers of machines B 
mean.machine.B <- mean(machine.B)
mean.machine.B

hist(machine.B)

sd.machine.B <- sd(machine.B)
sd.machine.B
```

With a mean of 3.12 machines needed to meet demand, we recommend having 4 of Machine B.

Since it requires one person to run both Machine A and B a total of 4 employees will be needed for those two types machines.


Next calculate values for machine C.

```{r}
# machine C
# import means and sds for manufacturing time for parts in machine A
means.C <- sturgill_manu$Machine.C.avg
sds.C <- sturgill_manu$Machine.C.sd

# calculate rnorm for all parts on machine C
time.C <- part.time(demands, means.C, sds.C)
mean(time.C)
sd(time.C)

# calculate number of machines needed
machine.C = time.C/capacity

# mean and sd for numbers of machines C 
mean.machine.C <- mean(machine.C)
mean.machine.C

sd.machine.C <- sd(machine.C)
sd.machine.C

hist(machine.C)

```

With a mean of  12.01 machines needed to meet demand, we recommend having 13 of Machine B. 

Since it requires one person to run each Machine C a total of 13 employees will be needed for those machines. Combined with the 4 employees required to operate type A & B machines, aa total of 17 employees would be needed.


Get employee count histogram

```{r}
# employee count
# add up machine time
employee.count <- machine.A/2 + machine.B/2 + machine.C


mean(employee.count)
sd(employee.count)
hist(employee.count)
```

The mean number employees doesn't take into account therounding up for each Machine type, but the histogram is useful for the spread of possible outcomes for employee count.