---
title: "ISQS-7339-sim-project-case-2"
author: "TQ Senkungu"
date: "4/26/2020"
output: word_document
---

In order to predict the numbers of machines and employees required to produce the planned production for the coming year, we use a monte carlo simulation with a normal distribution based on the mean and standard deviation given for the number of hours to produce each part and the amount of available time given the shop efficiency.

First import the data frame with project data and then set up a function for calculating the amount of production time required for production on each machine.

```{r}
# read in the csv with mean time and demand forecast data
sturgill_manu <- read.csv("https://raw.githubusercontent.com/tikisen/ISQS-7339-sim-project/master/Case%202/sturgill_manu.csv")

# set the seed
set.seed(1234)

# set the number of simulations
nsim = 1000000

demands <- sturgill_manu$Demand

part.time<- function(demand, mean, sd){
  total.time <- 0
  for (i in 1:length(demand)){
    total.time <- total.time + demand*rnorm(nsim, mean, sd)
  }
  return(total.time)
}
```

Up next is to calculate weekly capacity. We can use the normal distribution to determine a mean and sd for the capacity of the plant weekly production capacity.

```{r}
# set the seed
set.seed(1234)

# run the normal distribution times the total weekly hours available
capacity <- 120*rnorm(nsim, .7, .05)

# find the mean of the hours
capacity.mean <- mean(capacity)
capacity.mean

# find the std dev of the hours
capacity.sd <- sd(capacity)
capacity.sd

hist(capacity)

```

caclulate time for all parts for each machine

First calculate the values for machine A

```{r}
# set the seed
set.seed(1234)

# machine A
# import means and sds for manufacturing time for parts in machine A
means.A <- sturgill_manu$Machine.A.avg
sds.A <- sturgill_manu$Machine.A.sd

# calculate rnorm for all parts on machine A
time.A <- part.time(demands, means.A, sds.A)
mean(time.A)
sd(time.A)

# calculate number of machines needed
machine.A = time.A/capacity

# mean and sd for numbers of machines A 
mean.machine.A <- mean(machine.A)
mean.machine.A

sd.machine.A <- sd(machine.A)
sd.machine.A

hist(machine.A)
```

With a mean of 3.4 machines needed to meet demand, we recommend having 4 of Machine A.

Next, calculate values for machine B.

```{r}
# set the seed
set.seed(1234)

# machine B
# import means and sds for manufacturing time for parts in machine A
means.B <- sturgill_manu$Machine.B.avg
sds.B <- sturgill_manu$Machine.B.sd

# calculate rnorm for all parts on machine B
time.B <- part.time(demands, means.B, sds.B)
mean(time.B)
sd(time.B)

# calculate number of machines needed
machine.B = time.B/capacity

# mean and sd for numbers of machines B 
mean.machine.B <- mean(machine.B)
mean.machine.B

hist(machine.B)

sd.machine.B <- sd(machine.B)
sd.machine.B
```

With a mean of 3.12 machines needed to meet demand, we recommend having 4 of Machine B.

Since it requires one person to run both Machine A and B a total of 4 employees will be needed for those two types machines.


Next calculate values for machine C.

```{r}
# set the seed
set.seed(1234)

# machine C
# import means and sds for manufacturing time for parts in machine A
means.C <- sturgill_manu$Machine.C.avg
sds.C <- sturgill_manu$Machine.C.sd

# calculate rnorm for all parts on machine C
time.C <- part.time(demands, means.C, sds.C)
mean(time.C)
sd(time.C)

# calculate number of machines needed
machine.C = time.C/capacity

# mean and sd for numbers of machines C 
mean.machine.C <- mean(machine.C)
mean.machine.C

sd.machine.C <- sd(machine.C)
sd.machine.C

hist(machine.C)

```

With a mean of  12.01 machines needed to meet demand, we recommend having 13 of Machine B. 

Since it requires one person to run each Machine C a total of 13 employees will be needed for those machines. Combined with the 4 employees required to operate type A & B machines, aa total of 17 employees would be needed.


Get employee count histogram

```{r}
# employee count
# add up machine time
employee.count <- machine.A/2 + machine.B/2 + machine.C


mean(employee.count)
sd(employee.count)
hist(employee.count)
```

The mean number employees doesn't take into account therounding up for each Machine type, but the histogram is useful for the spread of possible outcomes for employee count.